### 2021-07-10 docs/manuscript/manuscript.tex
Improve description of supp. figs

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Response of GRNs to changes in morphogenetic field size.}
(A) Morphogen gradients of fields with 10, 20, 40 and 50 cells. (B) Fitness of the
GRNs in each one of the morphogenetic fields. (C) Principal Component Analysis
of fitness by morphogenetic field size. Although principal components separate
GRNs in clusters, not all the GRNs with the same topology are located in the
same group. (D) Average fitness of GRNs evolved in different morphogenetic
field sizes.

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Expression dynamics of main networks.}

@@

\paragraph*{S7 Fig.}
\label{S7_Fig}
{\bf Diffusion and degradation parameters.}
(A) Ternary plot showing the combination of diffusion parameters for genes A,
B and C. (B) Ternary plot showing the combination of degradation parameters
for genes A, B and C.

@@

\paragraph*{S2 Table.}
\label{S2_Table}
{\bf Average fitness of each topology in different morphogenetic fields.}
The average fitness by topology is reported for morphogenetic fields with 10, 20,
40 and 50 cells.

>>>>

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Response of GRNs to changes in morphogenetic field size.}
(A) Morphogen gradients of fields with 10, 20, 40 and 50 cells. (B) Fitness of the
GRNs by topology in each one of the morphogenetic fields. (C) Principal Component
Analysis of fitness by morphogenetic field size. Although principal components
separate GRNs in clusters, not all the GRNs with the same topology are located in the
same group. (D) Average fitness of GRNs evolved in different morphogenetic
field sizes.

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Expression dynamics of main networks.}
The dynamics of expression is shown from $t = 1$ to $t = 30$ for the eight most
abundant topologies. The red line
represents the expression level of the gene C along the morphogenetic field,
the blue line represents the expression level of gene B and
the dotted line represents the expression level of gene A.

@@

\paragraph*{S7 Fig.}
\label{S7_Fig}
{\bf Diffusion and degradation parameters.}
(A) Ternary plot showing the combination of diffusion parameters for genes A,
B and C. (B) Ternary plot showing the combination of degradation parameters
for genes A, B and C. The color gradient that goes from topology 1 in white to
topology 714 in black shows no distinguishable pattern.

@@

\paragraph*{S2 Table.}
\label{S2_Table}
{\bf Average fitness of each topology in different morphogenetic fields.}
The average fitness by topology is reported for morphogenetic fields with 10, 20,
40 and 50 cells. Data from this table are shown in \nameref{S3_Fig}B.
